\hypertarget{index_intro_sec}{}\section{Introduction}\label{index_intro_sec}
\hyperlink{class_s_o_d_a}{S\-O\-D\-A} is an Arduino library for data logging. It provides functions to simplify datalogging tasks using Olympia Circuit's \hyperlink{class_s_o_d_a}{S\-O\-D\-A} H\-E 1.\-0 board. \hyperlink{class_s_o_d_a}{S\-O\-D\-A} stands for Simple Open Data Acquisition. The goal of the project is to provide simple, high quality tools for the collection and analysis of environmental data. The library was built by Peter Gould (\href{mailto:peter@olympiacircuits.com}{\tt peter@olympiacircuits.\-com}). Some code was adapted from Petre Rodan's D\-S3231 library for Arduino. Additional thanks go to William Greiman for his S\-D\-\_\-\-F\-A\-T library.

The \hyperlink{class_s_o_d_a}{S\-O\-D\-A} library consists of a single class \hyperlink{class_s_o_d_a}{S\-O\-D\-A}. \hypertarget{index_dependencies_sec}{}\section{Dependencies}\label{index_dependencies_sec}
Sd\-Fat\-: library for S\-D card functions. This library needs to be added to your Arduino library along with \hyperlink{class_s_o_d_a}{S\-O\-D\-A}.

E\-E\-P\-R\-O\-M\-: standard Arduino library for E\-E\-P\-R\-O\-M functions (comes with your Arduino installation).

Wire\-: standard Arduino library for I2\-C communication (comes with your Arduino installation). \hypertarget{index_install_sec}{}\section{Installation}\label{index_install_sec}
The contents of the \hyperlink{class_s_o_d_a}{S\-O\-D\-A} folder should be added to the library folder of your Arduino installation (e.\-g., C\-:\textbackslash{}Program Files (x86)\textbackslash{}Arduino\textbackslash{}libraries). Arduino must be restarted after the library has been added. 